---
title: "Coffee ratings"
author: "Julia Müller"
date: "08 06 2021"
output: html_document
---

Welcome!

Data source: https://github.com/rfordatascience/tidytuesday/blob/2e9bd5a67e09b14d01f616b00f7f7e0931515d24/data/2020/2020-07-07/readme.md

Let's read in the data and get a first impression! The Tidy Tuesday site includes a link to read in the data and information on the variables. 


# Reading in the data, loading packages

```{r}
coffee <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

library(tidyverse)
```


# Exploring the data

```{r}
summary(coffee)

names(coffee)

str(coffee)

head(coffee)

skimr::skim(coffee)

coffee$altitude
```

Checklist
- What does each row contain?
  
- Are the data types correct?

- Messy or tidy data? Which variables, if any, are untidy?

Refer back to the codebook on github!

First impressions?


# Fixing data types

Convert species and country of origin from character to factor variables

```{r}
coffee %>% 
  mutate(species = as_factor(species),
         country_of_origin = as_factor(country_of_origin))

coffee <- coffee %>% 
  mutate(across(c(country_of_origin, species), as_factor))

str(coffee)
```


# Plots

Cup points by altitude
total_cup_points
altitude_mean_meters

Scatterplot (geom_point)
x-axis: altitude_mean_meters
y-axis: total_cup_points


```{r}

```



